---
title: "Code-through-assignemnt-Goel-527"
author: "Sunayna Goel"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: paged
    theme: cerulean
    highlight: textmate
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set( echo=TRUE, message=FALSE, warning=FALSE )
```

### Code Through Assignment


# Introduction 

**Text Mining** in R makes it possible to identify most frequently used keywords in a text paragraph. It allows a user to create **word cloud**, or **text cloud** as a visual representation of these keywords . **Word cloud** is a visually engaging and  powerful communication tool. Text mining packages such as **qunateda**, **tm**, **stringr** provide robust tools for text analysis by making it easy to manipulate data, manage corpus and analyse keywords. Packages **wordcloud** and **wordcloud2** make it possible to quickly visualise keywords as word-cloud. 

## Getting started 

The following packages and libraries are needed for this purpose. 
```{r}
# install.packages() cannot be included in an RMD file when knitting

#install.packages("quanteda")
#install.packages ("wordcloud")
#install.packages ("wordcloud2")
#install.packages("tidyverse")

#load_packages

library( quanteda )  ## Manage and analyse textual data
library(wordcloud)   ## Plots a cloud of words shared across documents
library(wordcloud2)  ## Provides traditional wordcloud with HTML5
library(tidyverse)   ## Includes popular packages used in data analyses
```

## Data download
For the purpose of this tutorial a local .txt is file is used. It is downloded in R using **read.table()** which convert .txt file to a datatable with two columns and seven rows in this case. First columns is just row numbers and second column has all the data. 

```{r results='hide'}
#Load local .txt file 
setwd( "/Users/sunaynaagarwal/Desktop" )
organic.text<- readLines("Textanalysis.txt",warn=FALSE )
organic.text
```

## Data Manipulation

In this step the text document is converted to lower case. It is then turned to **corpus** for data manipulation. Punctuation and filler words are removed. 

```{r results='hide'}

#convert in lower case
organic.text <- tolower (organic.text)

#make corpus
corp.organic <- corpus(organic.text)

#corpus content
corp.organic

# remove punctuation 
tokens <- tokens( corp.organic, what="word", remove_punct=TRUE )
head( tokens )

# remove filler words like the, and, a, to
tokens <- tokens_remove( tokens, c( stopwords("english"), "nbsp" ), padding=F )

head( tokens )

```

### Top keywords

Identify top 50 keywords. 
```{r}
#Top 10 token without stemming
my.matrix<-tokens %>% dfm( stem=F ) %>% topfeatures(n=50 )
head(my.matrix)

```
## Package Wordcloud

### Data Matrix

Convert the output in a matrix for generating the **Word Cloud**

```{r}
mat <- as.matrix(my.matrix)
my.frequency <- sort(rowSums(mat),decreasing=TRUE)
my.data <- data.frame(word = names(my.frequency),freq=my.frequency)
head(my.data, 7)
```

### Output Word Cloud

Wordcloud allows the user to generate cloud with keywords in random order or in non-random order keeping high frequency words towards the center. There are other arguments to adjust the colors and rotation of the keywords in the actual cloud. 

```{r }
# reproduces output
set.seed(101)
# generate word cloud using keywords at random
wordcloud(words = my.data$word, freq = my.data$freq, rot.per=0.30, colors=brewer.pal(7, "Dark2"), min.freq=4, max.words = 200, random.order=FALSE)
```

## Package Wordcloud2

### Data Table
Convert the output to a datatable for generating the **Word Cloud**


```{r}
#convert tokens to a datatable
my.df<-tokens %>% dfm( stem=F ) %>% topfeatures(n=50 )
data.table<- data.frame( word=names(my.df), freq=my.df,row.names=NULL )

```

### Output WordCloud
Wordcloud2 offer eveything that wordcloud offers plus more. It allows user to chnage background color and produce output in a distinctive shape. 

```{r}
# reproduces output
set.seed(1234)
wordcloud2(data= data.table, color=rep_len( c("forestgreen","darkcyan"), nrow(demoFreq)),size = 0.7, shape = 'pentagon',minRotation = -pi/8, maxRotation = -pi/8, rotateRatio = .7, backgroundColor = 'khaki')
```

## Acknowledgement

The following resources were used to create this tutorial for the assignment. To explore more please click the following links.   

[STHDA](http://www.sthda.com/english/wiki/text-mining-and-word-cloud-fundamentals-in-r-5-simple-steps-you-should-know)   

[cran.rstudio- WordCloud](https://cran.r-project.org/web/packages/wordcloud/wordcloud.pdf) 

[cran.rstudio- WordCloud2](https://cran.r-project.org/web/packages/wordcloud2/vignettes/wordcloud.html)  

[rGraph Gallery](https://www.r-graph-gallery.com/wordcloud.html)  

